### 2016-10-01 Chapters/ResponseTheory.tex
Change colorscheme and extract only neede stuff from classicthesis

Solvent relaxation is an important point when formulating response
properties. Solvation dynamics occurs on timescales and through
relaxation modes that are typical of the solvent molecular structure and of the
peculiar solute-solvent interactions.
This is clearly difficult to model with continuum models, since the
entire frequency spectrum of the permittivity $\diel(\omega)$ would be
required.\autocite{Ingrosso2003-ev, Caricato2005-lo,
Mennucci2005-vi, Caricato2006-ba, Corni2015-pe}
However, if one considers the initial steps of an electronic excitation
process, a Franck--Condon-like response of the solvent can be assumed.
Nuclear motions of the solute and solvent molecules alike will not be able to
follow the fast rearrangement of the electronic density, therefore the
corresponding part of the response will remain frozen in the state
immediately preceding the change.
Such an assumption, albeit approximate, leads to the following partition
of the polarization vector:
The polarization vector will then be (approximately) a sum of two
components:
\begin{equation}
 \vect{P} \simeq \vect{P}_\mathrm{fast} + \vect{P}_\mathrm{slow}.
\end{equation}
This is equivalent to considering only the asymptotic limits of the solvent
dielectric spectrum, \ie the static $\diels$ and optical
dielectric constants $\dield$.

>>>>

Solvent relaxation is an important point when formulating response
properties. Solvation dynamics occurs on timescales and through
relaxation modes that are typical of the solvent molecular structure and of the
peculiar solute-solvent interactions.
This is clearly difficult to model with continuum models, since the
entire frequency spectrum of the permittivity $\diel(\omega)$ would be
required.\autocite{Ingrosso2003-ev, Caricato2005-lo,
Mennucci2005-vi, Caricato2006-ba, Corni2015-pe}
However, if one considers the initial steps of an electronic excitation
process, a Franck--Condon-like response of the solvent can be assumed.
Nuclear motions of the solute and solvent molecules alike will not be able to
follow the fast rearrangement of the electronic density, therefore the
corresponding part of the response will remain frozen in the state
immediately preceding the change.
Such an assumption, albeit approximate, leads to the following partition
of the polarization vector:
The polarization vector will then be (approximately) a sum of two
components:
\begin{equation}
 \vect{P} \simeq \vect{P}_\mathrm{fast} + \vect{P}_\mathrm{slow}.
\end{equation}
This is equivalent to considering only the asymptotic limits of the solvent
dielectric spectrum, \ie the static $\diels$ and optical
dielectric constants $\dield$.\autocite{Aguilar1993-pu, Cammi1995-ah,
Cammi2005-tb, Corni2005-nd}

### 2016-10-01 FrontBackmatter/Colophon.tex
Titlepage done, microtype is in (thanks LuaLaTeX), text area similar to Tufte
Change colorscheme and extract only neede stuff from classicthesis

\pdfbookmark[1]{Colophon}{colophon}
\section*{Colophon}
This document was typeset using \XeLaTeX, with the
\texttt{classicthesis} template developed by André Miede.\footnote{\url{https://bitbucket.org/amiede/classicthesis/}}
The style was inspired by Robert Bringhurst's seminal book on typography
\emph{The Elements of Typographic Style}.\autocite{Bringhurst2004-wn}
The bibliography was processed using
Bib\LaTeX\footnote{\url{https://www.ctan.org/pkg/biblatex}} and
Biber.\footnote{\url{http://biblatex-biber.sourceforge.net/}}
TeX Gyre Termes provides both the text and display typeface.
\textsf{TeX Gyre Adventor} is the sans-serif typeface, while Jim Lyles's
\texttt{Bitstream Vera Mono} is used for monospaced text.
Finally, XITS acts as the math typeface.

>>>>

\pdfbookmark[1]{Colophon}{colophon}
\section*{Colophon}
This document was typeset using \LuaLaTeX, with a modified version of
the \texttt{classicthesis} template developed by André
Miede.\footnote{\url{https://bitbucket.org/amiede/classicthesis/}}
The style was inspired by Robert Bringhurst's seminal book on typography
\emph{The Elements of Typographic Style}\autocite{Bringhurst2004-wn}
and Edward Tufte's work.\autocite{Tufte1983-pr, Tufte1994-wf,
Tufte1997-fx, Tufte2006-ui}
The bibliography was processed using
Bib\LaTeX\footnote{\url{https://www.ctan.org/pkg/biblatex}} and
Biber.\footnote{\url{http://biblatex-biber.sourceforge.net/}}
TeX Gyre Termes provides both the text and display typeface.
\textsf{TeX Gyre Adventor} is the sans-serif typeface, while Jim Lyles's
\texttt{Bitstream Vera Mono} is used for monospaced text.
Finally, XITS is the typeface for mathematical formulas.
